pirouette: Quantifying the importance of a tree prior in Bayesian phylogenetics

### 2019-03-18 article.tex
Review ERQ4, progress https://github.com/richelbilderbeek/pirouette/issues/219

We agin specify we want all 40 inference models to compete, 
by calling \verb;create_all_experiments;,
as done in listing~\ref{lst:create_all_experiments}.

@@

@@

\begin{lstlisting}[language=R, floatplacement=ht, frame=single]
errors <- pir_run(
  phylogeny = phylogeny,
  pir_params = pir_params
)
\end{lstlisting}

@@

\begin{lstlisting}[language=R, floatplacement=ht, frame=single]
pir_plot(errors)
\end{lstlisting}

>>>>

We again specify we want all 40 inference models to compete, 
by calling \verb;create_all_experiments;,
as done in listing~\ref{lst:create_all_experiments}.

@@

\begin{lstlisting}[language=R, floatplacement=ht, frame=single]
pir_params <- create_pir_params(
  alignment_params = alignment_params,
  experiments = experiments,
  error_measure_params = error_measure_params,
  twinning_params = twinning_params
)
\end{lstlisting}
\richel{
  Refer to earlier listing for this call to \texttt{create\_pir\_params}
}

@@

\begin{lstlisting}[language=R, floatplacement=ht, frame=single]
errors <- pir_run(
  phylogeny = phylogeny,
  pir_params = pir_params
)
\end{lstlisting}
\richel{
  Refer to earlier listing for this call to \texttt{pir\_run}
}

@@

\begin{lstlisting}[language=R, floatplacement=ht, frame=single]
pir_plot(errors)
\end{lstlisting}
\richel{
  Refer to earlier listing for this call to \texttt{pir\_run}
}
